\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-11-11 chapters/0_abstract.tex
Add spectral exp; update Cityscapes sec. and App.
Small changes spectral clustering

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied. An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency. We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset. 
\end{abstract}

>>>>

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied. An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency. We compare GASP to spectral clustering methods on synthetic graphs and show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
\end{abstract}

### 2019-11-11 chapters/1_intro.tex
Small changes spectral clustering

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework. \TODO{Update CS and spectral clustering} 
It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
% Our code is available at \url{https://github.com/abailoni/GASP}.

>>>>

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework and 
it achieves competitive performance on CityScapes and the challenging CREMI 2016 segmentation benchmark.

In Sec. \ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods for signed graphs by testing it on synthetic graphs and neuron segmentation.

% Our code is available at \url{https://github.com/abailoni/GASP}.

### 2019-11-11 chapters/2_rel_work.tex
Small changes spectral clustering

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic}. % kulikov2018instance
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
\TODO{Add SSAP, predicting instance centers [Google+whatever], each instance one at the time, Seung paper}

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time. A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HAC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs. \TODO{Mention spectral methods}

>>>>

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; 
% SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}. % kulikov2018instance
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab}; in \cite{sofiiuk2019adaptis}, given a point $(x,y)$ in the image, the model generates the mask of the instance located at $(x,y)$.

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{Gao_2019_ICCV,liu2018affinity,xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time. A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs. 
Another line of reseatch is given by spectral clustering methods that, on the other hand, require the user to specify the number of clusters in advance. Recently, some of these methods have been generalized to graphs with signed weights \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral}, whereas others let the user specify must-link and cannot-link constraints between clusters \cite{rangapuram2012constrained,wang2014constrained,cucuringu2016simple}.

### 2019-11-11 chapters/5_experiments_cityscapes.tex
Small changes spectral clustering

Results on the \emph{test} set are summarized in Table \ref{tab:results_cityscapes_test}. The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model and then simply predict instance centers. The second best \emph{proposal-free} method is SSAP \cite{Gao_2019_ICCV}, which predicts long-range instance-affinities similarly to GMIS \cite{liu2018affinity}, but trains the model with extra side-losses. \algname{} with \emph{Average} linkage also achieves competitive results and outperforms the previous agglomeration method proposed in \cite{liu2018affinity}. Similarly to the experiments on neuron segmentation, results on the \emph{val} set (see Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}) show that other \algname{} linkage criteria tend to over-cluster, e.g. \emph{Abs Max}, or under-cluster and merge instances, e.g. \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the \emph{val} set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}. This is probably due to the fact that MultiStepHAC was tailored to the output affinities of the original model. 
Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.

>>>>

Results on the \emph{test} set are summarized in Table \ref{tab:results_cityscapes_test}. The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model to regress the centers of hte instances. The second best \emph{proposal-free} method is SSAP \cite{Gao_2019_ICCV}, which predicts long-range instance-affinities similarly to GMIS \cite{liu2018affinity}, but trains the model with extra side-losses. \algname{} with \emph{Average} linkage also achieves competitive results and outperforms the previous agglomeration method proposed in GMIS \cite{liu2018affinity}. Similarly to the experiments on neuron segmentation, results on the \emph{val} set (see Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}) show that other \algname{} linkage criteria tend to over-cluster, e.g. \emph{Abs Max}, or under-cluster and merge instances, e.g. \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the \emph{val} set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}. This is probably due to the fact that MultiStepHAC was tailored to the output affinities of the original model. 
Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.

### 2019-11-11 chapters/5_experiments_compare_rules.tex
Small changes spectral clustering

\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

>>>>

\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure*}
\centering
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    \end{subfigure}

        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
}\label{fig:noise_plots}
\end{figure*}
\begin{figure*}[t]
        \centering
\begin{minipage}[t]{0.31\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         Method & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averaged over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.3\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
        Method & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
        \end{tabular}
        \vspace*{0.99em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (November 2019). All entries, apart from our using \algname{}, employ superpixel-based post-processing pipelines.}
    \label{tab:results_cremi_test}
\end{minipage}\hfill
\begin{minipage}[t]{0.35\textwidth}
\centering
    \scriptsize
    \vspace*{-1.5em}
\begin{tabular}[t]{l|cc}
        \multirow{2}{*}{Method}    & AP  & AP 50\% \\ 
         & \multicolumn{2}{c}{(higher is better)} \\ \midrule
           Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
           UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
           SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
           AdaptIS \cite{sofiiuk2019adaptis} & 32.5 & 52.5 \\
           PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
           \textbf{GMIS Model \cite{liu2018affinity} + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
           JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
           \textbf{GMIS} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
           Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           % DWT \cite{bai2017deep} & 19.4 & 35.3 \\
           % InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
        \end{tabular}
    % \caption{CityScapes \emph{test} set}
    % \vspace*{0.6em}
    \captionof{table}{Results on CityScapes test. Methods marked with~$\dagger$ are \emph{proposal-based}. Only methods that do not use external training data (e.g. MS COCO) are shown.}\label{tab:results_cityscapes}
    \label{tab:results_cityscapes_test}
\end{minipage}
\end{figure*}

\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{figure*}[t]
\begin{minipage}{0.65 \textwidth}
\centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_6.pdf} % left bottom right top
\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image from the \emph{validation} set.}\label{fig:cityscapes}
\end{minipage}\hfill
\begin{minipage}{0.3 \textwidth}
    \centering
    \small
        \begin{tabular}[t]{l|cc}
             Agglomeration method & AP \\ \midrule
            % PANet \cite{liu2018path} & - & \textbf{36.5} \\
            % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
              \textbf{\algname{} Average}& \textbf{34.3} \\
              \algname{} Average + Constraints & 33.9 \\
             MultiStepHAC \cite{liu2018affinity} & 33.0 \\
              \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
              \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
              \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
        \end{tabular}
    \vspace*{0.6em}
    \captionof{table}{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model trained in \cite{liu2018affinity} and different graph agglomeration methods.}
    \label{tab:results_cityscapes_val}
\end{minipage}
\end{figure*}

\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score (\TODO{Fix link} https://cremi.org/leaderboard/), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

### 2019-11-11 chapters/5_experiments_noise.tex
Small changes spectral clustering

\subsection{Results and discussion}\label{sec:results}
\textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other. For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs. Max.) \cite{wolf2018mutex}. The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets. Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.56\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averages over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.4\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
        \end{tabular}
        \vspace*{1em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    \end{subfigure}

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
}\label{fig:noise_plots}
\end{figure}

>>>>

\subsection{Results and discussion}\label{sec:results}
\textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other. For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC \cite{keuper2015efficient} (\algname{} Sum), Greedy Fixation \cite{levinkov2017comparative} (\algname{} Sum + Constraints) or Mutex Watershed \cite{wolf2018mutex} (\algname{} Abs. Max.). The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets. Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.

### 2019-11-11 chapters/5_experiments_spectral.tex
Small changes spectral clustering

\section{Comparison with spectral clustering} 
In this section we compare \algname{} to spectral clustering methods for signed graphs both on synthetic graphs and real ones from neuron segmentation. These methods \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral} require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph. In the following comparison, we make these baselines as strong as possible by specifying the true number of clusters for the spectral methods.

@@

\begin{figure}
\centering
        \includegraphics[width=0.45\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf}
        \caption{Experiments on SSBM synthetic graphs \TODO{Update}}
    \label{fig:SSBM_spectral_experiments}
\end{figure}
\begin{table}
\centering
\begin{tabular}{l|c}
           Method & Rand-Score \\ \midrule
           \textbf{GASP Average} & \textbf{0.8966} \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \caption{Experiments on a tiny crop of the CREMI dataset, training sample B \TODO{Update}}
    \label{tab:cremi_spectral_experiments}
\end{table}

>>>>

\section{Comparison with spectral clustering} \label{sec:spectral_clust}
In this section we compare \algname{} to spectral clustering methods for signed graphs both on synthetic graphs and real ones from neuron segmentation. These methods require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph. In the following comparison, we make these baselines as strong as possible by specifying the true number of clusters for the spectral methods.

@@

\begin{figure}
\centering
        \includegraphics[width=0.45\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf}
        \caption{Performances of \algname{} compared to spectral clustering methods on SSBM synthetic graphs.}
    \label{fig:SSBM_spectral_experiments}
\end{figure}
\begin{table}
\centering
\footnotesize
\begin{tabular}{l|c}
           Method & Rand-Score \\ \midrule
           \textbf{GASP Average} & \textbf{0.8966} \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \caption{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
    \label{tab:cremi_spectral_experiments}
\end{table}
